### 2014-01-22 Draft/abstract.tex
fixed some reading group comments.
Fixed comments more comments

\begin{abstract}
Formal specifications of using a libraries Application Programming Interface (API)
can be used in conjunction with formal analysis tools such as
model checkers and runtime verifiers to assess the quality of a software.
Despite being highly desirable, most API's do not have formal specifications.
In contrast, API documents contain valuable information about the usage in natural language.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents
can be prohibitively time consuming and error prone.
To address this issue, we propose a natural language processing based automated approach \tool ,
to infer formal specifications from natural language text of API documents.
In particular, we focus on temporal constraints, that are defined as constraints on the
\textit{allowed sequence of invocations of methods within an API}.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of PP\% precision and RR\% recall
in inferring TT temporal constraints from more than ZZZZ sentences of API documents.

>>>>

\begin{abstract}
Formal specifications of using a libraries Application Programming Interface (API)
can be used in conjunction with formal analysis tools such as
model checkers and runtime verifiers to assess the quality of a software.
Despite being desirable, most API's do not have formal specifications.
In contrast, API documents contain valuable information about the usage in natural language.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents
can be prohibitively time consuming and error prone.
To address this issue, we propose a natural language processing based automated approach \tool ,
to infer formal specifications from natural language text of API documents.
In particular, we focus on temporal constraints, that are defined as constraints on the
\textit{allowed sequence of invocations of methods within an API}.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of 60\% precision and 80\% recall
in inferring 63 temporal constraints from more than 2400 sentences of API documents.

### 2014-01-22 Draft/approach.tex
Fixed comments more comments

\begin{figure}
	\centering
		\includegraphics[scale=0.45]{approach.eps}
	\caption{Overview of \tool\ framework}
	\label{fig:approachOverview}
\end{figure}

We next present our framework for inferring specifications from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of our framework.
Our framework consists of four major components: an API parser, a preprocessor, a text-analysis engine, and a postprocessor.

The API parser accepts online API description and extracts method descriptions.
The pre-processor accepts method descriptions and preprocesses the sentences in the descriptions, such as annotating sentence boundaries and reducing lexical tokens. 
The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation and then leverages the FOL representation of a sentence to infer specifications.
Finally, the postprocessor undoes any modifications done by the preprocessor to get refined specifications.

Besides the previously described major components the framework also consists of a an external component, namely target specification generator.
This component accepts the specification generated by our framework and using mapping functions to a target specification language generates specifications in the target language of choice.
We next describe each component in detail.

@@

The preprocessor accepts API method descriptions extracted by the parser and preprocesses the natural language text, to be further analyzed by the text-analysis engine.
The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ framework.
In particular, the preprocessor first employs the noun boosting followed by heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
From an implementation perspective, we chose the Stanford parser~\cite{SNLP}.
However, this component can be implemented using any other existing NLP libraries or frameworks.
In particular, we annotate each sentence with POS tags, named-entity Annotations and Stanford-typed dependencies.
For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

A key way of identifying reference to a method within the API in our proposed framework is the employment of a semantic graph of an API.
In particular, we propose to initially infer such graphs from API documents.
Manually creating a semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
We first consider the name of the class.
We then find the synonyms terms used refer to the class in question.
The synonym terms are listed as by breaking down the camel-case notation in the class name.
This list is further augmented by listing the name of the parent classes and implemented interfaces if any.

>>>>

\begin{figure}
	\centering
		\includegraphics[scale=0.45]{approach.eps}
	\caption{Overview of \tool\ approach}
	\label{fig:approachOverview}
\end{figure}

We next present our approach for inferring specifications from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of our approach.
Our approach consists of five major components: a preprocessor, a text-analysis engine, a semantic graph generator, specification extractor, and a type analyzer.

The pre-processor accepts API documents and preprocesses the sentences in the method description, such as annotating sentence boundaries and reducing lexical tokens.
The text-analysis engine accepts the pre-processed sentences and annotates them using an NLP parser.
The text-analysis engine further transforms the annotated sentences into the first-order-logic (FOL) representation.
Finally, the specification extractor then leverages the FOL representation of a sentence to infer specifications.
Finally, the postprocessor undoes any modifications done by the preprocessor to get refined specifications.

Besides the previously described major components the approach also consists of a an external component, namely target specification generator.
This component accepts the specification generated by our approach and using mapping functions to a target specification language generates specifications in the target language of choice.
We next describe each component in detail.

@@

The preprocessor accepts API method descriptions extracted by the parser and preprocesses the natural language text, to be further analyzed by the text-analysis engine.
The preprocessing steps are required to increase the accuracy core NLP techniques (described in Section~\ref{sub:CoreNLPback}) that are used in the subsequent phases of \tool\ approach.
In particular, the preprocessor first employs the noun boosting followed by heuristics listed under lexical token reduction, as introduced in Section~\ref{sub:SENLPback}.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence within each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
From an implementation perspective, we chose the Stanford parser~\cite{SNLP}.
However, this component can be implemented using any other existing NLP libraries or approachs.
In particular, we annotate each sentence with POS tags, named-entity Annotations and Stanford-typed dependencies.
For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

A key way of identifying reference to a method within the API in our proposed approach is the employment of a semantic graph of an API.
In particular, we propose to initially infer such graphs from API documents.
Manually creating a semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed previously in ~\cite{pandita13:WHYPER}) to infer such semantic graphs from API documents that can potentially be automated.
We first consider the name of the class.
We then find the synonyms terms used refer to the class in question.
The synonym terms are listed as by breaking down the camel-case notation in the class name.
This list is further augmented by listing the name of the parent classes and implemented interfaces if any.

### 2014-01-22 Draft/background.tex
Fixed comments more comments

\textbf{Co-reference Resolution}~\cite{RaghunathanEMNLP10,LeeCoNLL11}. Also known as \textit{`anaphora resolution'}, these techniques aim to identify multiple expressions present across (or within) the sentences, that point out to the same thing or \textit{`referant'}. These techniques are useful for extracting information; especially if the information encompasses many sentences in a document.

@@

\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However, as mentioned earlier, POS tagging work well on well written news articles which does not necessary entail that they work well with domain specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

>>>>

%\textbf{Co-reference Resolution}~\cite{RaghunathanEMNLP10,LeeCoNLL11}. Also known as \textit{`anaphora resolution'}, these techniques aim to identify multiple expressions present across (or within) the sentences, that point out to the same thing or \textit{`referant'}. These techniques are useful for extracting information; especially if the information encompasses many sentences in a document.

@@

\textbf{Noun Boosting}~\cite{pandita12:inferring}. Accurate annotation of POS tags in a sentence is fundamental to effectiveness of any advanced NLP technique.
However, as mentioned earlier, POS tagging work well on well written news articles which does not necessary entail that the tagging works well on domain specific text as well.
Thus, noun boosting is a necessary precursor to application of POS tagging on domain specific text.
In particular, with respect to API documents certain words have a very different semantic meaning, in contrast to general linguistics that causes incorrect annotation of POS tags.

### 2014-01-22 Draft/introduction.tex
Fixed comments more comments

Temporal specifications~\cite{slam-2002} of an Application Programming Interface (API) 
describe allowed sequences of invocations of methods within an API. 
These specifications govern the secure and robust operation of client software 
using these APIs.
If these specifications are formal (machine-readable such as code-contracts),
they can be used  as a basis of formal analysis tools such 
as model checker and runtime verifiers
in detecting the violations of these temporal constraints as defects.

@@

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
Existing approaches focus in inferring method pre-post conditions~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} in terms of parameter constraints either using static or dynamic analysis techniques.
Furthermore, there is a class of NLP based approaches~\cite{pandita12:inferring, wu2013inferring} that infer constraints from API documents.
However, similar to static and dynamic analysis techniques, these approaches focus on parameter constraints as well.  
In contrast, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods.

Although, in typed languages some sequencing constraints are enforced by type system. 
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).  However, most temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.

Our proposed approach address the following challenges to infer temporal constraints automatically from natural language text.
First, relying just on type information will result in a incomplete list of temporal constraints. 
Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
for a strongly typed language.
The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
Our proposed approach extends the existing approaches to address the challenge.

>>>>

Temporal specifications~\cite{ball2002s} of an Application Programming Interface (API) 
describe allowed sequences of invocations of methods within an API. 
These specifications govern the secure and robust operation of client software 
using these APIs.
If these specifications are formal (machine-readable such as linear temporal logic),
they can be used  as a basis of formal analysis tools such 
as model checker and runtime verifiers
in detecting the violations of these temporal constraints as defects.

@@

% Combine first two sentences
% In contrast, temporal constraints are beyond these parameter constraints. may be use difficult to express using parameter constraints
% Amazon S3 is popularly used web service for simple cloud based storage
There are existing approaches focus on inferring just the method pre-post conditions in terms of parameter constraints either using program analysis techniques~\cite{Henkel07discoveringdocumentation,Ghezzi:2009:SIB:1555001.1555057,Henkel:2008:DDA:1363102.1363105,Flanagan:2001:HAA:647540.730008,Buse:2008:ADI:1390630.1390664} or using NLP~\cite{pandita12:inferring, wu2013inferring}. 
In contrast, temporal constraints are beyond these parameter constraints.
Temporal constraints, in general focus on rules related to orchestration of methods within an API rather than focusing on the requirements on the input parameters of these methods. Our proposed approach addresses the following challenges to infer temporal constraints automatically from API documents.

First, relying just on type information will result in a incomplete list of temporal constraints. 
Although, in typed languages some temporal constraints are enforced by type system. 
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
However, temporal constraints are not limited by the type definitions (i.e, requirements on the type of input parameters), and are currently expressed mostly in natural language in API documents, as described in the example previously.
We propose to address the issue by augmenting the type definitions based temporal constraints with the the constraints inferred from
the natural language text in API documents.
%Furthermore, such constraints although valuable but are already checked by any advanced Integrated Development Environment(IDE) such as eclipse
%for a strongly typed language.
%The problem is exacerbated in web based API's such as \amazonAPI\ where most of the types are either \CodeIn{integer} or \CodeIn{strings}.
%Our proposed approach extends the existing approaches to address the challenge.
